Methods and Results

### 2021-03-29 ms.Rmd
Writing

```{r loadpackages, echo = FALSE, results = "hide"}
  pacman::p_load(tidyverse, metafor, brms, metaAidR, ape, phytools, metaAidR)

@@

# Models
  model <- rma.mv(SMDH ~ 1, V = data$v_SMDH, random = list(~1|study, ~1|obs, ~1|variable, ~1|species), test = "t", data = data)

  I2(model, v = data$v_SMDH, phylo = FALSE)

  model <- rma.mv(SMDH ~ 1, V = data$v_SMDH, random = list(~1|study, ~1|obs, ~1|variable, ~1|species, ~1|species2), R = list(species = phylogeny), test = "t", data = data)

  model <- rma.mv(SMDH ~ SSD_lnRR, V = data$v_SMDH, random = list(~1|study, ~1|obs, ~1|species), R = list(species = phylogeny), test = "t", data = data)

  model <- rma.mv(SMDH ~ Harm_type-1, V = data$v_SMDH, random = list(~1|study, ~1|species, ~1|obs), R = list(species = phylogeny), test = "t", data = data)
  robust(model, cluster = data$study)

  model <- rma.mv(SMDH ~ Harm_type + SSD_lnRR, V = data$v_SMDH, random = list(~1|study, ~1|obs, ~1|species), R = list(species = phylogeny), test = "t", data = data)
  robust(model, cluster = data$study)

  model <- rma.mv(SMDH ~ Gestation + SSD_lnRR, V = data$v_SMDH, random = list(~1|study, ~1|obs, ~1|species), R = list(species = phylogeny), test = "t", data = data)
  robust(model, cluster = data$study)

@@

>>>>

```{r loadpackages, echo = FALSE, results = "hide"}
  pacman::p_load(tidyverse, metafor, brms, metaAidR, ape, phytools, metaAidR, orchaRd)

@@

# Models
  model1.1 <- rma.mv(SMDH ~ 1, V = data$v_SMDH, random = list(~1|study, ~1|variable, ~1|species, ~1|obs), test = "t", data = data)

hetero_table <-  I2(model1.1, v = data$v_SMDH, phylo = FALSE)

  model1.2 <- rma.mv(SMDH ~ 1, V = data$v_SMDH, random = list(~1|study, ~1|variable, ~1|species, ~1|species2, ~1|obs), R = list(species = phylogeny), test = "t", data = data)

hetero_table_phylo <-  I2(model1.2, v = data$v_SMDH, phylo = "species")

  model1.3 <- rma.mv(SMDH ~ SSD_lnRR, V = data$v_SMDH, random = list(~1|study, ~1|obs, ~1|species), R = list(species = phylogeny), test = "t", data = data)

  model1.4 <- rma.mv(SMDH ~ Harm_type-1, V = data$v_SMDH, random = list(~1|study, ~1|species, ~1|obs), R = list(species = phylogeny), test = "t", data = data)
  robust(model1.4, cluster = data$study)

  model1.5 <- rma.mv(SMDH ~ Harm_type + SSD_lnRR, V = data$v_SMDH, random = list(~1|study, ~1|obs, ~1|species), R = list(species = phylogeny), test = "t", data = data)
  robust(model1.5, cluster = data$study)

  model1.6 <- rma.mv(SMDH ~ Gestation + SSD_lnRR, V = data$v_SMDH, random = list(~1|study, ~1|obs, ~1|species), R = list(species = phylogeny), test = "t", data = data)
  robust(model1.6, cluster = data$study)

@@

#### Manipulating direct and indirect female harm negatively impacts female fitness

Experimentally manipulating female harm resulted in a strong decrease in female fitness overall (i.e., positive effect size with control group females having higher fitness than treatment groups: `r model1.1$beta`, 95% CI: `r model1.1$ci.lb` to `r model1.1$ci.ub`, $n_{effects}$ = `r model1.1$k.all`, $n_{study}$ = `r model1.1$s.nlevels[1]`). Even when accouting for sampling variance there was high effect size heterogeneity ($I^2_{Total}$ = `r hetero_table$I2_Est.[nrow(hetero_table)]`, 95% CI: `r hetero_table[nrow(hetero_table), "2.5% CI"]` to `r hetero_table[nrow(hetero_table), "97.5% CI"]`) with most variance being the result of between study ($I^2_{Study}$ = `r hetero_table$I2_Est.[1]`, 95% CI: `r hetero_table[1, "2.5% CI"]` to `r hetero_table[1, "97.5% CI"]`) and between species ($I^2_{Species}$ = `r hetero_table$I2_Est.[3]`, 95% CI: `r hetero_table[3, "2.5% CI"]` to `r hetero_table[3, "97.5% CI"]`) effects. The trait type and phylogeny explained much less variation overall ($I^2_{Trait}$ = `r hetero_table$I2_Est.[2]`, 95% CI: `r hetero_table[2, "2.5% CI"]` to `r hetero_table[2, "97.5% CI"]`; $I^2_{Phylogeny}$ = `r hetero_table_phylo$I2_Est.[5]`, 95% CI: `r hetero_table_phylo[5, "2.5% CI"]` to `r hetero_table_phylo[5, "97.5% CI"]`).
